Learning Programs through Bayesian Inference and Planning

### 2013-10-23 drafts/nips/nips2013.tex
Added new bibliography file. Added some figures.

\section{Application to Structure Learning}

@@

\section{Building Towers in Blocks World}

@@

\bibliographystyle{plain}
\bibliography{nips2013}

>>>>

\section{Application to Graphical Model Structure Learning}

Learning the structure of graphical models that capture the independencies underlying a dataset is an active area of research\cite{adams-wallach-ghahramani-2010a}\cite{ISI:000240797500002}\cite{ISI:000178037200004}\cite{ISI:A1995RX35400001}. Graphical model structures enforce the conditional independences a modeler believes exists among latent and observed random variables\cite{DBLP:books/daglib/0066829}.

@@

\begin{figure}
\begin{minipage}[c][8cm][t]{.4\textwidth}
  \vspace*{\fill}
  \includegraphics[width=\linewidth]{./figures/tasks.pdf}
  \caption{test figure one}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}[c][8cm][t]{.3\textwidth}
  \vspace*{\fill}
  \fbox{\includegraphics[width=\linewidth]{./figures/GraphCombinators.pdf}}
  \caption{test figure two}
  \label{fig:test2}\par\vfill
  % \includegraphics[width=5cm,height=4.5cm]{im
  \caption{test figure three}
  \label{fig:test3}
\end{minipage}
\end{figure}
\section{Building Towers in Blocks World}

@@

\bibliographystyle{plain}
\bibliography{eyal_bib}
